Disparities in Climate-Induced Health Outcomes in the Greater Toronto Area.

### 2022-07-07 outputs/paper/paper.qmd
Update paper.qmd

## Visualizing Pollution from 2002-2020

### Visualizing Pollution by Year

@@

#### Visualizing NO (Nitric Oxide) by Year

@@

#### Visualizing NO2 (Nitrogen Dioxide) by Year

@@

#### Visualizing O3 (Ozone) by Year

@@

#### Visualizing CO (Carbon Monoxide) by Year

#### Visualizing SO2 (Sulfur Dioxide) by Year

#### Visualizing Pollution by Month

pollution %>% ggplot(
  aes(x = factor(month_name, level = level_order), y = mean_pollution, color = pollutant)) + geom_point() + 
  labs(color="Pollutant") + xlab("Month") + ylab("Mean Pollution (ppb)")

#### Visualizing NO (Nitric Oxide) by Month

pollution %>% filter(pollutant == "NO") %>% ggplot(
  aes(x = factor(month_name, level = level_order), y = mean_pollution, color = pollutant)) + geom_point() + 
  labs(color="Pollutant") + xlab("Month") + ylab("Mean Pollution (ppm)")

#### Visualizing NO2 (Nitrogen Dioxide) by Month

pollution %>% filter(pollutant == "NO2") %>% ggplot(
  aes(x = factor(month_name, level = level_order), y = mean_pollution, color = pollutant)) + geom_point() + 
  labs(color="Pollutant") + xlab("Month") + ylab("Mean Pollution (ppm)")

#### Visualizing O3 (Ozone) by Month

@@

#### Visualizing CO (Carbon Monoxide) by Month

@@

pollution %>% filter(pollutant == "CO") %>% ggplot(
  aes(x = factor(month_name, level = level_order), y = mean_pollution, color = pollutant)) + geom_point() + 
  labs(color="Pollutant") + xlab("Month") + ylab("Mean Pollution (ppm)")

#### Visualizing SO2 (Sulfur Dioxide) by Month

@@

pollution %>% filter(pollutant == "SO2") %>% ggplot(
  aes(x = factor(month_name, level = level_order), y = mean_pollution, color = pollutant)) + geom_point() + 
  labs(color="Pollutant") + xlab("Month") + ylab("Mean Pollution (ppm)")

>>>>

## Visualizing Pollution from 2002-202

@@

pollution %>% ggplot(
  aes(x = factor(month_name, level = level_order), y = mean_pollution, color = pollutant)) + geom_point() + 
  labs(color="Pollutant") + xlab("Month") + ylab("Mean Pollution (ppb)")
```

#### Visualizing NO (Nitric Oxide)

@@

pollution %>% filter(pollutant == "NO") %>% ggplot(
  aes(x = factor(month_name, level = level_order), y = mean_pollution, color = pollutant)) + geom_point() + 
  labs(color="Pollutant") + xlab("Month") + ylab("Mean Pollution (ppm)")
```

#### Visualizing NO2 (Nitrogen Dioxide)

@@

pollution %>% filter(pollutant == "NO2") %>% ggplot(
  aes(x = factor(month_name, level = level_order), y = mean_pollution, color = pollutant)) + geom_point() + 
  labs(color="Pollutant") + xlab("Month") + ylab("Mean Pollution (ppm)")
```

#### Visualizing O3 (Ozone)

@@

@@

#### Visualizing CO (Carbon Monoxide)

@@

pollution %>% filter(pollutant == "CO") %>% ggplot(
  aes(x = factor(month_name, level = level_order), y = mean_pollution, color = pollutant)) + geom_point() + 
  labs(color="Pollutant") + xlab("Month") + ylab("Mean Pollution (ppm)")
```

#### Visualizing SO2 (Sulfur Dioxide)

@@

pollution %>% filter(pollutant == "SO2") %>% ggplot(
  aes(x = factor(month_name, level = level_order), y = mean_pollution, color = pollutant)) + geom_point() + 
  labs(color="Pollutant") + xlab("Month") + ylab("Mean Pollution (ppm)")
```
